Updates on the Exoplanet Orbit Database

### 2013-12-28 draft/ms.tex
Fill all table fields except for a few data types. Update makefile.

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}

@@

NAME\dotfill & String & Name of planet &  \\
OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet &  \\
COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) &  \\
HD\dotfill & Long Integer & Henry Draper number of sar &  \\
HR\dotfill & Integer & Bright Star Catalog number of star &  \\
HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of star & \\
SAO\dotfill & Long Integer & SAO catalog number of star & \\
GL\dotfill & Float & GJ or Gliese catalog number of star & \\

@@

sexagesimal string & \\

@@

sexagesimal string & \\
KEPID\dotfill & & & \\
KOI\dotfill & & & \\
KDE\dotfill & & & \\
EOD\dotfill & & & \\
MICROLENSING\dotfill & & & \\ 
IMAGING\dotfill & & & \\
TIMING\dotfill & & & \\
ASTROMETRY\dotfill & & & \\

@@

BMV\dotfill & Float & $B-V$ color & \\

@@

J\dotfill & Float & $J$ magnitude & \\
H\dotfill & Float & $H$ magnitude & \\
KS\dotfill & Float & $K_S$ magnitude & \\
DIST\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\

@@

star & -UPPER,-LOWER,U-,-REF,-URL \\
GAMMA\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\

@@

PER\dotfill & Double & Orbital period in days & -UP-,-LOWER,U-,-REF,-URL \\
ECC\dotfill & Float & Orbital eccentricity & -UPPER,-LOWER,U-,-REF,-URL \\
OM\dotfill & Float & Argument of periastron in degrees & -UPPER,-LOWER,U-,-REF,-URL \\
K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER,-LOWER,U-,-REF,-URL \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER,-LOWER,U-,-REF,-URL \\

@@

systems only ZZZ still true?) & -UPPER,-LOWER,U-,-REF,-URL \\

@@

function) in $M_{\rm Jup}$ & -UPPER,-LOWER,U-,-REF,-URL \\
A\dotfill & Float & Orbital semimajor axis in AU & -UPPER,-LOWER,U-,-REF,-URL \\
MASS\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
SEP\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
TREND\dotfill  & Boolean & Linear trend in fit? & \\
LAMBDA\dotfill & Float & Projected spin-orbit misalignment & -UPPER,-LOWER,U-,-REF,-URL \\
BIGOM\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \\

@@

DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER,-LOWER,U-,-REF,-URL \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER,-LOWER,U-,-REF,-URL \\

@@

HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPE-,-LOWE-,U-,-REF,-URL \\
AR\dotfill & $(a/R_*)$ & & -UPPER,-LOWER,U-,-REF,-URL \\
B\dotfill & Float & Impact parameter of transit & -UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

calculated from transit parameters &
-UPPER,-LOWER,U-,-REF,-URL \\
TRANSIT\dotfill & Boolean & Is the planet known to transit? & TRANSITREF,TRANSITURL \\
DR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
RR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\

@@

SE\dotfill & & & -REF,-URL \\
SEDEPTHJ\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\
SEDEPTHH\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\
SEDEPTHKS\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\
SEDEPTHKP\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\
SEDEPTH36\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\
SEDEPTH45\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\
SEDEPTH58\dotfill & & & 
-UPPER,-LOWER,U-,-REF,-URL \\
SEDEPTH80\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\
SET\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
& & & \\

@@

RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \\
CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \\
NOBS\dotfill & Integer & Number of observations used in fit & \\
NCOMP\dotfill & Integer & Number of planetary companions known & \\
MULT\dotfill & Boolean & Multiple planets in system? & \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \\

@@

planet in the system & \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \\
ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \\

@@

STAR\dotfill & & & \\
MSTAR\dotfill & Float & Mass of host star & -UPPER,-LOWER,U-,-REF,-URL \\
RSTAR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER,-LOWER,U-,-REF,-URL \\
RHOSTAR\dotfill & & &
-UPPER,-LOWER,U-,-REF,-URL \\

@@

host star & -UPPER,-LOWER,U-,-REF,-URL \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER,-LOWER,U-,-REF,-URL \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \\
KP\dotfill & & & \\
SPECREF\dotfill & & & SPECURL \\

@@

ETDNAME\dotfill & String & Name of host star used in the Exoplanet

@@

SIMBADNAME\dotfill & String & Valid SIMBAD name of host star & SIMBADURL \\
EANAME\dotfill & & & EAURL \\

>>>>

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}

@@

NAME\dotfill & String & Name of planet & \nodata \\
OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet & \nodata \\
COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of
star & \nodata \\
SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\
GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\

@@

sexagesimal string & \nodata  \\

@@

sexagesimal string & \nodata \\
KEPID\dotfill & & The unique \kepler\ star identifier & \nodata \\
KOI\dotfill & & KOI object number & \nodata \\
KDE\dotfill & Boolean & If true, then this planet appears in the
\kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, then this planet has been vetted by the
exoplanets.org team & \nodata \\
MICROLENSING\dotfill & Boolean & If true, then this planet was detected via microlensing & \nodata \\ 
IMAGING\dotfill & Boolean & If true, then this planet was detected via imaging
& \nodata \\
TIMING\dotfill & Boolean & If true, then this planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, then this planet was detected via
astrometric motion & \nodata \\

@@

BMV\dotfill & Float & $B-V$ color & \nodata \\

@@

J\dotfill & Float & $J$ magnitude & \nodata \\
H\dotfill & Float & $H$ magnitude & \nodata \\
KS\dotfill & Float & $K_S$ magnitude & \nodata \\
DIST\dotfill & & Distance to planetary system based on parallax in parsecs & -UPPER, etc. \\

@@

star in k\mps & -UPPER, etc. \\
GAMMA\dotfill & & Systemic radial velocity in k\mps & -UPPER, etc. \\

@@

PER\dotfill & Double & Orbital period in days & -UPPER, etc. \\
ECC\dotfill & Float & Orbital eccentricity & -UPPER, etc. \\
OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. \\
K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER, etc. \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\

@@

systems only ZZZ still true?) & -UPPER, etc. \\

@@

function) in $M_{\rm Jup}$ & -UPPER, etc. \\
A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
MASS\dotfill & & & -UPPER, etc. \\
SEP\dotfill & & & -UPPER, etc. \\
TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees & -UPPER, etc. \\
BIGOM\dotfill & & Longitude of ascending node in degrees & -UPPER, etc. \\
FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\

@@

DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER, etc. \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\

@@

HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\
R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPER, etc. \\
AR\dotfill & $(a/R_*)$ & & -UPPER, etc. \\
B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\

@@

-UPPER, etc. \\

@@

calculated from transit parameters in cgs unit &
-UPPER, etc. \\
TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
DR\dotfill & & Distance during transit in stellar radii & -UPPER, etc. \\
RR\dotfill & & $(R_p/R_*)$ & -UPPER, etc. \\

@@

SE\dotfill & Boolean & If true, at least one secondary eclipse has been detected in the wavelengths listed below & -REF,-URL \\
SEDEPTHJ\dotfill & & The secondary eclipse depth measured in the near
infrared J band centered at 1.25 \micron &
-UPPER, etc. \\
SEDEPTHH\dotfill & & The secondary eclipse depth measured in the near
infrared H band centered at 1.65 \micron & 
-UPPER, etc. \\
SEDEPTHKS\dotfill & & The secondary eclipse depth measured in the near
infrared Ks band centered at 2.15 \micron &
-UPPER, etc. \\
SEDEPTHKP\dotfill & & The secondary eclipse depth measured in the
Kepler photometry band in the optical from 400 to 865 nm &
-UPPER, etc. \\
SEDEPTH36\dotfill & & The secondary eclipse depth measured by
\spitzer\ in its IRAC1 band centered at 3.6 \micron &
-UPPER, etc. \\
SEDEPTH45\dotfill & & The secondary eclipse depth measured by \spitzer\
in its IRAC2 band centered at 4.5 \micron &
-UPPER, etc. \\
SEDEPTH58\dotfill & & The secondary eclipse depth measured by \spitzer\
in its IRAC2 band centered at 5.8 \micron & 
-UPPER, etc. \\
SEDEPTH80\dotfill & & The secondary eclipse depth measured by \spitzer\
in its IRAC2 band centered at 8.0 \micron &
-UPPER, etc. \\
SET\dotfill & & ZZZ Epoch of secondary eclipse center in
HJD\tablenotemark{c}$-2,440,000$ ZZZ & -UPPER, etc. \\
& & & \\ % empty row so that next table section starts on new page

@@

RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \nodata \\
CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\
NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\

@@

planet in the system & \nodata \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\

@@

STAR\dotfill & String & Standard name for host star & \nodata \\
MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
RSTAR\dotfill & & Radius of host star in solar radii & -UPPER, etc. \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
RHOSTAR\dotfill & & Density of host star & -UPPER, etc. \\

@@

host star in cgs unit & -UPPER, etc. \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
KP\dotfill & & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & & Source of most of the spectroscopic parameters
listed for convenience & SPECURL \\

@@

ETDNAME\dotfill & String & Name of planet used in the Exoplanet

@@

SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
planet, if available) & SIMBADURL \\
EANAME\dotfill & String & Name of planet used in the Exoplanet
Archive database & EAURL \\
